Forecasting the 2024 U.S. Presidential Election: A Poll-Based Approach

### 2024-11-04 paper/paper.qmd
Updated plots

This study leverages a dataset of polling data for the 2024 U.S. Presidential Election, focusing on predicting support for the two main candidates, Kamala Harris and Donald Trump. Each entry in the dataset represents results from individual polls, capturing both the timing and geographical scope of polling, which is crucial for analyzing national trends and state-specific shifts, particularly in key swing states. By collating data from multiple polling sources, the dataset captures a broad snapshot of voter sentiment across the country, reflecting variations across time, poll methodologies, and geographic regions.

@@

## Electoral Vote Projections
Integrating the swing state projections with solid state predictions, the Primary Model estimates the electoral vote totals for each candidate. Kamala Harris is projected to win 292 electoral votes, surpassing the 270-vote threshold required to secure victory. Donald Trump, by comparison, is projected to receive 246 electoral votes. This projection, based on aggregating state-level outcomes, suggests that Harris has a favorable chance of achieving the necessary electoral college majority if current polling trends continue. The model indicates that Harris’s projected wins in swing states like Wisconsin, Michigan, and Pennsylvania could be critical to her securing an electoral majority.

@@

```{r}
#| echo: false
#| message: false
#| warning: false
solid_state_votes <- data.frame(
  Candidate = c("Harris", "Trump"),
  Solid_State = c(226, 219)
)

@@

# View the results
kable(total_votes, caption = "Predicted Electoral Votes for Each Candidate")

>>>>

This study leverages the dataset of polling data for the 2024 U.S. Presidential Election, focusing on predicting support for the two main candidates, Kamala Harris and Donald Trump. Each entry in the dataset represents results from individual polls, capturing both the timing and geographical scope of polling, which is crucial for analyzing national trends and state-specific shifts, particularly in key swing states. By collating data from multiple polling sources, the dataset captures a broad snapshot of voter sentiment across the country, reflecting variations across time, poll methodologies, and geographic regions.

@@

## Electoral Vote Projections
Integrating the swing state projections with solid state predictions, the Primary Model estimates the electoral vote totals for each candidate. Kamala Harris is projected to win 292 electoral votes, surpassing the 270-vote threshold required to secure victory. Donald Trump, by comparison, is projected to receive 246 electoral votes, as shown in @tbl-res and @fig-result .This projection, based on aggregating state-level outcomes, suggests that Harris has a favorable chance of achieving the necessary electoral college majority if current polling trends continue. The model indicates that Harris’s projected wins in swing states like Wisconsin, Michigan, and Pennsylvania could be critical to her securing an electoral majority.

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: tbl-res
#| tbl-cap: Predicted Electoral Votes for Each Candidate
solid_state_votes <- data.frame(
  Candidate = c("Harris", "Trump"),
  Solid_State = c(226, 219)
)

@@

# View the results
kable(total_votes)
